---
title: "Learining R3"
author: "Kristina Matthiesen Hansen"
format: html
---


```{r setup}
library(fs)
library(tidyverse)
library(dplyr)
library(here)
source(here("R/functions.R"))
source(here::here("R/functions.R"))
```

# Session-section

Importing new data

Snakecase er den bedste måde at gøre det på - det ser pænere ud

```{r importdata}
#| eval: false
#| include: false
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
``` 

## Exercise: Reading other files.
```{r}
#| eval: false
#| include: false
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
```


New participant 
```{r new}
#| eval: false
#| include: false

here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case
  )
```
```{r}
#| eval: false
#| include: false
here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
```

```{r function}
#' Add two numbers together
#'
#' @param num1 A number here.
#' @param num2 A number here.
#'
#' @returns Returns the sum of two numbers.
#'
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}
```

```{r}
#| eval: false
#| include: false
#' Read in one nurses-stress data file
#'
#' @param file_path
#'
#' @returns A path to a data file
#' @export outputs a data frame/tibble
#'
#' @examples
read <- function(file_path) {
  data <- file_path |>
    read_csv(
      show_col_types = FALSE,
      name_repair = to_snake_case,
      n_max = 100
    )
  return(data)
}
```

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") |>
  read()
```

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()
```


```{r 100rows}
# Outputs only 100 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()


# Her er det en defalut at der bliver loadet 100 rows, hvis ikke man selv specificerer hvor mange rækker man ønsker fx max_rows = 1050


# Outputs only 100 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()

# Outputs only 1000 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 1000)

# Outputs all rows (`Inf` means infinity)
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = Inf)
```

## Using map 
```{r map}
hr_files <- here("data-raw/nurses-stress/") |>
  dir_ls(regexp = "HR.csv.gz", recurse = TRUE)

hr_files


hr_data <- hr_files |>
  map(read) |>
  list_rbind(names_to = "file_path_id")

hr_data
```

### Noter til ovenstående øvelse 
Hvis jeg gerne vil læse om en funktion ? foran 
File_path_id bruges til at hente stilen ind for hvert ID gennem mappen de er placeret i. 
Dette kan laves om til et unikt ID nummer for hvert individ, baseret på den unikke sti de tilhører.


## Exercise: Convert map to function and use on sleep.
```{r}
#| eval: false
#| include: false
#' Map function
#'
#' @param filename
#'
#' @returns all the datafiles combined together
#'
read_all <- function(filename) {
  files <- here::here("data-raw/nurses-stress/") |>
    fs::dir_ls(regexp = filename, recurse = TRUE)

  data <- files |>
    purrr::map(read) |>
    purrr::list_rbind(names_to = "file_path_id")

  return(data)
}

read_all

read_all("HR.csv.gz")
read_all("IBI.csv.gz")
```

## Inspecting the data

```{r}
hr_data <- read_all("HR.csv.gz")
survey_data <- here("data-raw/nurses-stress/survey-results.csv.gz") |>
  read()

hr_data
survey_data
```

them main reason we can't joun the two datasets togehter, is that the survey_data have ID's and the hr_data have folder paths instead - so we dont know wich values fits to wich id


```{r}
hr_data |>
  mutate(
    id = str_extract(
      file_path_id,
      pattern = "/stress/[:alnum:]{2}/"
    ) |>
      str_remove("/stress/") |>
      str_remove("/"),
    .before = file_path_id
  ) |>
  select(-file_path_id)
```
```{r}
#| eval: false
#| include: false
#|
#' Creating function for getting ID
#'
#' @returns data with id
#'
get_participant_id <- function(data) {
  data_with_id <- data |>
    dplyr::mutate(
      id = stringr::str_extract(
        file_path_id,
        pattern = "/stress/[:alnum:]{2}/"
      ) |>
        stringr::str_remove("/stress/") |>
        stringr::str_remove("/"),
      .before = file_path_id
    ) |>
    dplyr::select(-file_path_id)
  return(data_with_id)
}

get_participant_id(hr_data)
```


## Working with across

```{r}
hr_data <- read_all("HR.csv.gz") |>
  get_participant_id()

hr_data
```

```{r}
hr_data |>
  summarise(across(where(is.numeric), list(
    mean = mean,
    median = median,
    sd = sd
  ))) # = tilføjer et label i dette tilfølde
```

## Working with dates
```{r}
hr_data |>
  mutate(
    datetime = round_date(collection_datetime,
      unit = "minute"
    ),
    .before = collection_datetime
  )
```

## Summerising by groups 

```{r}
hr_data |>
  mutate(
    collection_datetime = round_date(
      collection_datetime,
      unit = "minute"
    )
  ) |>
  summarise(
    across(
      where(is.numeric),
      list(mean = mean, sd = sd, median = median)
    ),
    .by = c(id, collection_datetime)
  )
```


## making a funktion for the summerise funktion
```{r}
#| eval: false
#| include: false
#' Making a summerise function
#'
#' @param data
#'
#' @returns summerise in collums

#'
summarise_by_datetime <- function(data) {
  summarised_data <- data |>
    dplyr::mutate(
      collection_datetime = lubridate::round_date(
        collection_datetime,
        unit = "minute"
      )
    ) |>
    dplyr::summarise(
      dplyr::across(
        tidyselect::where(is.numeric),
        list(mean = mean, sd = sd, median = median)
      ),
      .by = c(id, collection_datetime)
    )
  return(summarised_data)
}

summarise_by_datetime(hr_data)
```


## Prepare HR data
```{r}
#| eval: false
#| include: false
hr_data <- read_all("HR.csv.gz") |>
  get_participant_id() |>
  summarise_by_datetime()

ibi_data <- read_all("IBI.csv.gz") |>
  get_participant_id() |>
  summarise_by_datetime()

temp_data <- read_all("TEMP.csv.gz") |>
  get_participant_id() |>
  summarise_by_datetime()

bvp_data <- read_all("BVP.csv.gz") |>
  get_participant_id() |>
  summarise_by_datetime()

eda_data <- read_all("EDA.csv.gz") |>
  get_participant_id() |>
  summarise_by_datetime()
```


## Pivit longer 
```{r}
survey_data <- here("data-raw/nurses-stress/survey-results.csv.gz") |>
  read()
survey_data
```

```{r}
survey_tidy <- survey_data |>
  mutate(
    date = mdy(date),
    start_datetime = as_datetime(paste(date, start_time)),
    end_datetime = as_datetime(paste(date, end_time)),
    datetime_id = start_datetime,
    .before = start_time
  ) |>
  select(-c(date, start_time, end_time, duration))
```
```{r}
survey_tidy |>
  select(id, datetime_id, start_datetime, end_datetime) |>
  pivot_longer(c(start_datetime, end_datetime), names_to = NULL, values_to = "collection_datetime") |>
  group_by(pick(-collection_datetime)) |>
  complete(collection_datetime = seq(min(collection_datetime),
    max(collection_datetime),
    by = 60
  )) |>
  ungroup()


# names_to fjerner name collum
```



```{r}
#| eval: false
#| include: false
#' Tidy up the dates in the survey results
#'
#' @param data
#'
#' @returns tidyed dataset
#'
tidy_survey_dates <- function(data) {
  tidied <- data |>
    dplyr::mutate(
      date = lubridate::mdy(date),
      start_datetime = as_datetime(paste(date, start_time)),
      end_datetime = as_datetime(paste(date, end_time)),
      datetime_id = start_datetime,
      .before = start_time
    ) |>
    dplyr::select(-c(date, start_time, end_time, duration))
  return(tidied)
}
```




```{r Tidy-up-survey-results}
#| eval: false
#| include: false
#' Maked the dataset longer
#'
#' @param data
#'
#' @returns longer dataset
#'
survey_to_long <- function(data) {
  longer <- data |>
    dplyr::select(id, datetime_id, start_datetime, end_datetime) |>
    tidyr::pivot_longer(c(start_datetime, end_datetime), names_to = NULL, values_to = "collection_datetime") |>
    dplyr::group_by(pick(-collection_datetime)) |>
    tidyr::complete(collection_datetime = seq(min(collection_datetime),
      max(collection_datetime),
      by = 60
    )) |>
    ungroup()
  return(longer)
}
```






```{r}
#| eval: false
#| include: false
survey_long |> 
  left_join(survey_tidy)

survey_tidy |> 
  count()

survey_tidy |> 
  count(id, datetime_id) |> 
  filter(n>1)


survey_long |> 
  right_join(survey_tidy)

survey_long |> 
  full_join(survey)
```

```{r}
#| eval: false
#| include: false
nurses_stress <- survey_long |> 
  full_join(survey_tidy) |> 
  full_join(hr_data)

nurses_stress |> 
  arrange(id, collection_datetime) |> 
  view()

nurses_stress


```



